draft_yma

### 2021-12-14 draft_yma.Rmd
transformation

# Global
skimr::skim(cdi_descriptive) %>% 
  select(-c("skim_type","complete_rate")) %>% 
    mutate(skim_variable = 
             recode(skim_variable, pcincome = "pcincome (in dollars)", totalinc = "totalinc (in million of dollars)"
  )) %>% 
  knitr::kable(
    col.names = c("variable", "n_missing", "mean","sd","min","Q25","median","Q75","max","histogram"),
    caption = "Global Summary", digits = 4)
```

@@

library(ggcorrplot)
library(ggstatsplot)
ggstatsplot::ggcorrmat(
  data = cdi,
  type = "parametric", # parametric for Pearson, nonparametric for Spearman's correlation
  colors = c("darkred", "white", "steelblue") # change default colors
)
```

@@

included pop in addition to pop18, pop65. Do we need pop tho? Would pop18 and pop65 be enough already?

did not include cty, state, area, crimes, totalinc, totalinc (included pcincome), do we need to include any of those? for example, both totalinc and pcincome, area and pop_den

@@

# use 
full_fit = lm(crm_1000 ~ ., data = cdi_model)
summary(full_fit)
```

@@

>>>>

# Global
skimr::skim(cdi_descriptive) %>% 
  select(-c("skim_type","complete_rate")) %>% 
    mutate(skim_variable = 
             recode(skim_variable, pcincome = "pcincome (in dollars)", totalinc = "totalinc (in million of dollars)"
  )) %>% 
  knitr::kable(
    col.names = c("variable", "n_missing", "mean","sd","min","Q25","median","Q75","max","histogram"),
    caption = "Global Summary", digits = 4)

ggplot(gather(cdi_descriptive), aes(value)) + 
    geom_histogram(bins = 13) + 
    facet_wrap(~key, scales = 'free_x')
```

@@

library(ggcorrplot)
library(ggstatsplot)
ggstatsplot::ggcorrmat(
  data = cdi_descriptive,
  type = "parametric", # parametric for Pearson, nonparametric for Spearman's correlation
  colors = c("darkred", "white", "steelblue") # change default colors
)
```

@@

@@

# use 
full_fit = lm(crm_1000 ~ ., data = cdi_model)
summary(full_fit)

ols_plot_resid_qq(full_fit)
ols_plot_resid_fit(full_fit)
```

## Transformation
```{r}
lambda = MASS::boxcox(full_fit)
optlam = lambda$x[which.max(lambda$y)]
optlam
```

The lambda from the transformation is 0.5454, so we will try to fit a square root transformation to y

```{r}
trans_fit = lm(crm_1000^0.5 ~ .,data = cdi_model)
summary(trans_fit)

ols_plot_resid_fit(trans_fit)
ols_plot_resid_qq(trans_fit)

lambda_trans = MASS::boxcox(trans_fit)
optlam_trans = lambda_trans$x[which.max(lambda_trans$y)]
lambda_trans
```

@@

boxcox

```{r}
lambda = boxcox(cdi_model$crm_1000~1)
optlam = lambda$x[which.max(lambda$y)]
```
